ESRC SDAI Application

### 2019-06-19 case_for_support.tex
Anna update

\textit{The problem is that we don't know the address of the young offenders. Could we the location info on where they committed the offences as a proxy of the LSOA where they live? not sure if this is viable;
defining a gang member is problematic in the crime data - if something serious is committed probably only one of them will be charged with it;
I was trying to identify children who were victims of something happening at an address where DA happened and perpetrated by a DA offender - it's very narrow and excludes children who *just* witnessed abuse}

>>>>

\textit{The problem is that we don't know the address of the young offenders. Could we the location info on where they committed the offences as a proxy of the LSOA where they live? not sure if this is viable;
defining a gang member is problematic in the crime data - if something serious is committed probably only one of them will be charged with it, maybe we should just concentrate on criminal activities;
I was trying to identify children who were victims of something happening at an address where DA happened and perpetrated by a DA offender - it's very narrow and excludes children who *just* witnessed abuse; however, the location id doesn't seem to specific to one place - one id can correspond to a road, dwelling, shop etc.}

There's a children's questionnaire, and they ask about gang membership. However, the sample size is very low (3,100 for the whole country).
